Forcing for Isabelle

### 2018-12-21 LICS/isabelle.tex
comentarios sobre Isar

>>>>

\medskip
\fbox{Portar a \textbf{Isabelle2018} antes de enviar.}

\fbox{Hacer benchmark para compararlos.}

\medksip

The source code is written for the 2018 version of Isabelle (with
minor modifications, it can be run in Isabelle2016-1). Most of it is
presented in the (nowadays standard) declarative flavour called
\emph{Isar} \cite{DBLP:conf/tphol/Wenzel99}, where intermediate
statements in the course 
of a proof are explicitly stated, interspersed with automatic 
tactics handling more trivial steps. The goal is that the resulting
text, a \emph{proof document}, can be understood without the need of
running it.
